\LARGE \bf Energy-Aware Dynamic Mission Planning Algorithm for UAVs

### 2020-10-15 icra-2021.tex
the sketch of the algorithm

%% pseudocode package
%\usepackage{algorithmic}

@@

@@

Let us consider a Fourier series $h:\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}$ of an arbitrary order $r\in\mathbb{Z}_{\geq 0}$ for the purpose of energy modeling of the mission
\begin{equation}\label{eq:fourier}
  h(t)=\sum_{n=0}^{r}{a_n\cos{\frac{nt}{\xi}}+b_n\sin{\frac{nt}{\xi}}},
\end{equation}
where $\xi\in\mathbb{R}$ is the characteristic time, and $a_n, b_n\in\mathbb{R}$ the Fourier series coefficients.

@@

Let us further define $g:\mathbb{Z}_{\geq 0}\times\mathbb{Z}_{\geq 0}\rightarrow\mathbb{R}_{\geq 0}$ as the instantaneous energy value obtained interrogating \powprof{}. The instantaneous computational energy component can be defined
\begin{equation}\label{eq:energy-comp}\begin{split}
  y_k^c:&=g\left(\text{QoS}_{k,0},\dots,\text{QoS}_{k,\sigma-1}\right)=g\left(\mathbf{s}_{k}\right).\\
\end{split}\end{equation}

@@

\subsection{Deployment algorithm}

>>>>

%% pseudocode package
%\usepackage{algorithmic}
\usepackage{algpseudocode}

@@

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}

\algdef{SE}[DOWHILE]{Do}{doWhile}{\algorithmicdo}[1]{\algorithmicwhile\ #1}%

@@

Let us consider a Fourier series $h:\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}$ of an arbitrary order $r\in\mathbb{Z}_{\geq 0}$ for the purpose of energy modeling of the mission
\begin{equation}\label{eq:fourier}
  h(t)=\sum_{n=0}^{r}{a_n\cos\left({nt/\xi}\right)+b_n\sin{\left({nt/\xi}\right)}},
\end{equation}
where $\xi\in\mathbb{R}$ is the characteristic time, and $a_n, b_n\in\mathbb{R}$ the Fourier series coefficients.

@@

Let us further define $g:\mathbb{Z}_{\geq 0}\times\mathbb{Z}_{\geq 0}\rightarrow\mathbb{R}_{\geq 0}$ as the instantaneous energy value obtained interrogating \powprof{}. The instantaneous computational energy component can be defined
\begin{equation}\label{eq:energy-comp}\begin{split}
  y_k^s:=g\left(\text{QoS}_{k,0},\dots,\text{QoS}_{k,\sigma-1}\right)=g\left(\mathbf{s}_{k}\right).\\
\end{split}\end{equation}

@@

\subsection{Output constraints set}

Recall the model in Equation~(\ref{eq:state-perf}). We stated the output $y_k$--the instantaneous energy consumption--evolves in $\mathbb{R}_{\geq 0}$. This is generally untrue. Physical UAVs are bounded by strict battery limitations.

Let us hence consider the state of charge (SoC) of such battery with a simplistic difference equation~\cite{seewald2020mechanical}
\begin{equation}\begin{split}
  \mathrm{SoC}_k=-\left(V-
  \sqrt{
    V^2-
    4R\tilde{V}y_kV^{-1}}
  \right)/2RQ_c,\\ 
\end{split}\end{equation}
where $V\in\mathbb{R}$ is the internal battery and $\tilde{V}\in\mathbb{R}$ the stabilized voltage, $R\in\mathbb{R}$ the resistance, and $Q_c\in\mathbb{R}$ the constant nominal capacity. We define the output constraints set
\begin{equation}
  \mathbb{Y}_k:=\{y_k\mid y_k\in[0,\mathrm{SoC}_kQ_cV]\subseteq{\mathbb{R}_{\geq 0}}\},
\end{equation}
where $\overline{\mathbb{Y}}_k$ is the maximum discharge capacity by the internal battery voltage--the maximum instantaneous energy.
\subsection{Deployment algorithm}

\begin{center}\textit{Ok, so I need to fix this algorithm properly. But the sketch is there (the position is missing but I'll make a wrapper tomorrow morning)!}\end{center}

\begin{algorithmic}[1]
  \Procedure{}{$\mathcal{M}_1$, $\mathbf{p}_1$, $\mathbf{q}_1$, $K$, $v$, $\varepsilon$}
  \State $k\gets 2$
  \State $\mathbf{z}_{k-1},\hat{\mathbf{q}}_{k-1}\gets \mathbf{q}_1$
  \State $\mathbf{v}_{k-1},\mathbf{u}_{k-1}\gets {\mathbf{u}_{k-1}(\overline{\mathbf{u}}_{k-1}^a,\mathbf{u}_{k-2}^a)}$
  \While{$k \leq t_f$}
    \Do
      \State $\mathbf{v}\gets\argmax_{\mathbf{v}}{\sum_{i=k-1}^{k+N-2}}{l(\mathbf{z}_i,\mathbf{v}_i)+V_f(\mathbf{z}_{N+1})}$
      \State $\mathbf{u}_{k-1}\gets \mathbf{v}+K(\hat{\mathbf{q}}_{k-1}-\mathbf{z}_{k-1})$
      \State $\hat{\mathbf{q}}_k^-\gets A\hat{\mathbf{q}}_{k-1} + B\mathbf{u}_{k-1}$
      \If{$C\hat{\mathbf{q}}_k^-\notin\mathbb{Y}_k$}
        \State $\mathbf{u}^a_{k-1}\gets\mathbf{u}^a_{k-1}/\overline{\mathbf{u}}^a_{k-1}$
        \State $\mathbf{v}_{k-1},\mathbf{u}_{k-1}\gets {\mathbf{u}_{k-1}(\overline{\mathbf{u}}_{k-1}^a,\mathbf{u}_{k-2}^a)}$

      \EndIf
    \doWhile{$C\hat{\mathbf{q}}_k^-\notin\mathbb{Y}_k$}

    \If{$\abs{y_k^m-C\hat{\mathbf{q}}_k^-}\leq \varepsilon$}
      \State $\hat{\mathbf{q}}_k\gets\hat{\mathbf{q}}_k^-$
    \Else 
      \State $P_k^-\gets AP_{k-1}A^T+Q$
      \State $L\gets P_k^-C^T/(CP_k^-C^T+R)$
      \State $\hat{\mathbf{q}}_k\gets \hat{\mathbf{q}}_k^-+L(y_k^m-C\hat{\mathbf{q}}_k^-)$
      $\mathbf{z}_{k-1}$
      \State $P_k\gets(I+LC)P_k^-$
    \EndIf
    \State $\mathbf{z}_k\gets A\mathbf{z}_{k-1}+B\mathbf{u}_{k-1}$
    \State $\mathbf{y}\gets\mathbf{y}\cup C\hat{\mathbf{q}}_k$
    \State $k\gets k + 1$
  \EndWhile % <---
  %\State $r\gets a\bmod b$
  %\State $\mathcal{M}_1\gets a\bmod b$
  %\While{$r\not=0$}\Comment{We have the answer if r is 0}
  %State $a\gets b$
  %\State $b\gets r$
  %\State $r\gets a\bmod b$
  %\EndWhile\label{euclidendwhile}
  %\State \textbf{return} $b$\Comment{The gcd is b}
  \EndProcedure
\end{algorithmic}
